\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

However, unlike the gradient drift case mentioned in Sec. \ref{subsec:GenGradDescent}, it is not possible to express the right hand side of \eqref{NewPDE} as the Wasserstein gradient of the functional \eqref{LyapButNotProx}. The latter is defined as \cite[Ch. 8]{ambrosio2008gradient} 
$$\nabla^{\text{Wasserstein}}\Phi := -\nabla\cdot\left(\rho\nabla\dfrac{\delta\Phi}{\delta\rho}\right),$$
where $\nabla$ denotes the standard Euclidean gradient w.r.t. the vector $(\bm{\xi},\bm{\eta})^{\top}$, and $\frac{\delta}{\delta\rho}$ denotes the functional derivative. From \eqref{FunctionalDerivative}, \eqref{defvectorfieldv} and \eqref{firstequality} in Appendix A, it is clear that the vector field $\bm{v}$ defined in \eqref{defvectorfieldv} is not equal to the negative of $\nabla\dfrac{\delta\Phi}{\delta\rho}$. Thus, even though the functional \eqref{LyapButNotProx} decreases along the transient solution of \eqref{NewPDE}, we cannot interpret it as the Wasserstein gradient flow of the functional \eqref{LyapButNotProx}.

@@

>>>>

However, unlike the gradient drift case mentioned in Sec. \ref{subsec:GenGradDescent}, it is not possible to express the right hand side of \eqref{NewPDE} as the Wasserstein gradient of the functional \eqref{LyapButNotProx}. The latter is defined as \cite[Ch. 8]{ambrosio2008gradient} 
$$\nabla^{\text{Wasserstein}}\Phi := -\nabla\cdot\left(\rho\nabla\dfrac{\delta\Phi}{\delta\rho}\right),$$
where $\nabla$ denotes the standard Euclidean gradient w.r.t. the vector $(\bm{\xi},\bm{\eta})^{\top}$, and $\frac{\delta}{\delta\rho}$ denotes the functional derivative. From \eqref{FunctionalDerivative}, \eqref{defvectorfieldv} and \eqref{firstequality} in Appendix A, it is clear that the vector field $\bm{v}$ defined in \eqref{defvectorfieldv} is not equal to the negative of $\nabla\dfrac{\delta\Phi}{\delta\rho}$. Thus, even though the functional \eqref{LyapButNotProx} decreases along the transient solution of \eqref{NewPDE}, we cannot interpret the flow generated by \eqref{TransformedPDEivp} as the Wasserstein gradient flow of the functional \eqref{LyapButNotProx}. Thus, in \eqref{InfiniteDimProxOpDef}, we cannot construct $(\Phi,{\rm{dist}})$ by pairing \eqref{LyapButNotProx} with the Wasserstein metric.

To set up a variational recursion of the form \eqref{InfiniteDimProxOpDef} for \eqref{TransformedPDEivp}, we set $(\Phi,{\rm{dist}}) \equiv \left(\widetilde{\Phi},\widetilde{W}\right)$ where
\begin{align}
\widetilde{\Phi}(\tilde{\rho}) := \int_{\mathbb{T}^{n} \times \mathbb{R}^{n}}\left(F(\boldsymbol{\eta})+\frac{1}{2} \log \tilde{\rho}\right) \tilde{\rho}\: \mathrm{d} \boldsymbol{\xi} \mathrm{d} \boldsymbol{\eta},
\label{Phitilde}	
\end{align}
and 
\begin{align}
\widetilde{W}^{2}\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right):=&\inf _{\pi \in \Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)}\!\int_{\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}}\!\!\left\{\left\|\overline{\boldsymbol{\eta}}-\boldsymbol{\eta}+h \nabla_{\boldsymbol{\xi}} U(\boldsymbol{\xi})\right\|_{2}^{2}\right.\nonumber\\
&\hspace*{-0.2in}\left.+12\left\|\frac{\overline{\boldsymbol{\xi}}-\boldsymbol{\xi}}{h}-\frac{\overline{\boldsymbol{\eta}}+\boldsymbol{\eta}}{2}\right\|_{2}^{2}\right\} \mathrm{d} \pi(\boldsymbol{\xi}, \boldsymbol{\eta}, \overline{\boldsymbol{\xi}}, \overline{\boldsymbol{\eta}}).
\label{Wtilde}	
\end{align}
In \eqref{Wtilde},

That the sequence of functions $\{\tilde{\varrho}_{k}\}$ for $k\in\mathbb{N}$, generated by the proximal recursion
\begin{align}
\tilde{\varrho}_{k} = {\text{prox}}^{{\rm{dist}}}_{h\widetilde{\Phi}}(\tilde{\varrho}_{k-1}), \quad k\in\mathbb{N}, \quad \varrho_{0}(\bm{x}) := \rho_{0}(\bm{x})
\label{KineticProx}	
\end{align}

was established in \cite{duong2014conservative}.

@@

% ==== M.H. Duong's prox for mixed conservative-dissipative =====

\bibitem{duong2014conservative}
M.H.~Duong, M.A.~Peletier, and J.~Zimmer, ``Conservative-dissipative Approximation Schemes for A Generalized Kramers Equation", \emph{Mathematical Methods in the Applied Sciences}, Vol. 37, No. 16, pp. 2517--2540, 2014.
